\begin{abstract}
Computer Use Agents (CUAs) represent a significant advancement in autonomous systems, combining Vision-Language Models for perception with constrained function calling for reliable execution. While these agents can perform virtually any action a human user can, this capability introduces complex security challenges that transcend traditional threat models. This paper examines the security landscape of CUAs through concrete attack scenarios, revealing a fundamental tension: CUAs can be exploited through behaviors that are \emph{entirely reasonable} given their available information. We argue that assigning security responsibility to CUAs is problematic when attacks succeed by exploiting goal-seeking behavior or the inherent temporal gap between observation and action. To address this, we propose integrating environmental defenses---URL reputation systems, clickjacking detection, and verification mechanisms---as queryable tools within the CUA's action space, enabling agents to access security-relevant information they cannot otherwise obtain. Furthermore, we reframe taint tracking as a conceptual framework for CUA security, arguing that traditional static analysis is fundamentally inapplicable to systems where all information flows through opaque neural inference. Under this framework, trust becomes a property of information flowing through the agent's reasoning process, and ``sanitization'' corresponds to verification steps that gate high-consequence actions. This conceptual approach provides principled guidance for designing CUA architectures that balance the autonomy essential to agent effectiveness with the safeguards necessary for secure operation.
\end{abstract}