\section{Threats To Validity}

There are several potential threats to the validity of our evaluation of \tool{}. First, the construction of the dataset could introduce biases. While we combined multiple existing benchmarks to create a comprehensive dataset, there is a possibility that the selected toxic and benign prompts may not fully represent the diversity of real-world prompts. This could affect the generalizability of our findings. Additionally, the benign prompts were sourced from ShareGPT, which may contain prompts that are not entirely representative of typical user interactions across different platforms.

Second, the experimental settings, such as the choice of LLMs and the configuration of the baselines, could influence the results. We selected popular open-source LLMs and configured them according to their respective instructions; however, variations in model performance across different versions or implementations could impact the comparability of our results. Furthermore, the performance of \tool{} might vary when integrated with other LLMs or used in different application contexts.

Lastly, the training and evaluation process itself could pose threats to validity. Although we conducted multiple runs to mitigate randomness and used standard metrics to evaluate performance, the inherent variability in machine learning experiments means that results could fluctuate slightly. Additionally, the specific settings for the classifier training, such as the learning rate and batch size, were chosen based on our preliminary experiments and might not be optimal for all scenarios. Future work should explore these parameters further to ensure the robustness of \tool{}'s performance.
