% Experimental results.
\providecommand{\tbd}{\textemdash}

\section{Evaluation}
\label{sec:evaluation}

\subsection{Experimental setup}
This section should describe the datasets, models, optimizers, training budgets, and hyperparameter search spaces used for each method. When reporting results, include enough detail to reproduce the runs (e.g., seed list, learning rate, batch size, and regularization coefficients).

\subsection{Main results}
Report the main comparison table(s) here, typically including:
\begin{itemize}
  \item baseline (no explicit regularization),
  \item classical regularizers (weight decay, dropout, etc.),
  \item neural balancing (before training and/or interleaved),
  \item combinations (e.g., weight decay + balancing).
\end{itemize}

\subsection{Regularization comparison on MNIST with a fully connected network}
\label{subsec:reg-mnist-fcn}
Table~\ref{tab:regularization-mnist-fcn} compares regularization methods after selecting each method's own hyperparameters on a \emph{validation} split using a unified protocol. Everything below is shared across methods except the meaning of each method's grid point (the knob being swept).

\paragraph{Validation-based hyperparameter protocol (GP Bayesian optimization).}
Hyperparameters are selected on a validation split using Gaussian-Process (GP) Bayesian optimization; the test set is used only for final numbers in Table~\ref{tab:regularization-mnist-fcn}. Here, Bayesian optimization (BO) is a sample-efficient search method for expensive black-box objectives (mean validation accuracy after training): it uses a GP surrogate to predict promising regions and an Expected-Improvement acquisition rule to balance exploration and exploitation, and one BO step in this report means evaluating one candidate configuration across the fixed seed list. The protocol is:
\begin{itemize}
  \item \textbf{Shared training protocol:} identical dataset splits, architecture, optimizer type, learning rate, batch size, maximum epochs, and early-stopping rule (when applicable), unless a row is explicitly ablating one of these.
  \item \textbf{Validation-only selection:} we hold out a validation subset of the training data (e.g.\ $\ValSplitPct\%$ of training examples, stratified by class). Bayesian optimization targets mean validation accuracy; test labels are never used during search.
  \item \textbf{Globally fixed random seeds (not tuned):} before any search, we fix one seed list (here: $\{\SeedList\}$, i.e., \NumSeeds{} seeds). Every BO candidate for every method is trained once per seed in this list. Seeds are not hyperparameters and are never selected for performance.
  \item \textbf{Surrogate model and acquisition:} for each method, we fit a GP surrogate over that method's hyperparameter space (continuous knobs are optimized in log space where appropriate) and select the next trial by Expected Improvement.
  \item \textbf{Equal BO trial budget per tunable method:} each tunable method receives the same number of BO candidates (\BOBudgetTotal{} total: \BOBudgetInit{} initial random points + \BOBudgetGuided{} GP-guided points). One candidate evaluated across the fixed seed list is counted as one BO step. The plain baseline has no tunable regularization coefficient and is therefore evaluated once (with the same seed list).
  \item \textbf{Search domains:} $L_2$ decay coefficient $\lambda_2 \in [10^{-5}, 3\cdot10^{-3}]$, $L_1$ penalty coefficient $\lambda_1 \in [10^{-5}, 3\cdot10^{-3}]$, dropout rate $p \in [0,0.5]$, early-stopping patience $K \in [5,20]$ (integer), and balancing schedule treated as a categorical variable over predefined modes (no balancing, pre-balance only, and selected interleaving frequencies).
  \item \textbf{Selection and reporting:} for each method, the chosen configuration is the one with the highest mean validation accuracy across the fixed seed list among all BO-evaluated candidates. The table reports test metrics for that chosen configuration only, with uncertainty (e.g.\ $\sigma_{\mathrm{test}}$) computed across the same seeds.
\end{itemize}

\paragraph{Limitation (BO still has design choices).}
Using GP BO avoids hand-crafted fixed grids, but fairness still depends on choices such as search-domain bounds, acquisition function, initialization strategy, and total BO budget. Different choices can change the selected hyperparameters and, in turn, final ranking.

\paragraph{Fixed experimental setting.}
Dataset: MNIST (official train/test split; $\MnistTrainSize{}$ training and $\MnistTestSize{}$ test images).
Inputs: grayscale $28\!\times\!28$ flattened to $784$; ToTensor scaling to $[0,1]$ followed by per-channel normalization to $[-1,1]$ (mean $0.5$, std.\ $0.5$), as implemented in the code.
Architecture: \texttt{small\_fcn} fully connected network, $784 \rightarrow 256 \rightarrow 10$, ReLU activations on the hidden layer, linear output (10 classes).
Optimization: stochastic gradient descent (SGD) without momentum, learning rate $\LearningRate$, batch size $\BatchSize$.
Regularization control: each row uses the backbone above with regularizer hyperparameters \emph{selected on the validation split} by GP BO in this subsection (plain uses $\lambda_2=0$, no dropout, no balancing).
Training: maximum $\MaxEpochs$ epochs per run; rows without early stopping train for the full budget; the early-stopping row uses the patience $K$ selected on validation by BO.
Target for convergence speed: test accuracy threshold $\tau = \TargetTauPct\%$; \emph{Epochs@$\tau$} is the first epoch (1-based index) at which test accuracy reaches or exceeds $\tau$.
Reproducibility: the seed list is fixed \emph{a priori} (see above); $\sigma_{\mathrm{test}}$ is the standard deviation of final test accuracy across those seeds for the selected configuration.

\input{tables/regularization_mnist_fcn}

\subsection{Data-scarce regime}
Because regularization effects are often most visible when data is limited, include a controlled ablation where the training set is reduced (e.g., 1\%, 5\%, 10\% of the full training data) while keeping the test set unchanged.

\subsection{Ablations}
Suggested ablations:
\begin{itemize}
  \item balancing cost choice: $L_1$ vs.\ $L_2$,
  \item balancing schedule: before training vs.\ every $k$ epochs,
  \item model size: small vs.\ medium vs.\ large,
  \item interaction with weight decay and dropout.
\end{itemize}

