% Main report introduction (regularization + neural balancing focus).

\section{Introduction}

Deep neural networks can fit complex functions, but this flexibility comes with a persistent risk of overfitting and fragile training dynamics. \emph{Regularization} refers to the broad set of techniques used to improve generalization, stabilize optimization, and impose inductive biases that better match the task and data regime.

This report studies the impact of several regularization approaches on neural network performance and training behavior. Beyond widely used techniques (e.g., weight decay and dropout), a main focus is \emph{synaptic neural balance} (``neural balancing'') as described in \texttt{reference/} \citep{alexos2025synapticbalance}. Neural balancing is distinctive in that it performs a structured re-scaling of weights intended to reduce a chosen weight ``cost'' while preserving the network's input--output function under common conditions (e.g., homogeneous activations).

\subsection{What we compare}
We organize the compared approaches into practical families:
\begin{itemize}
  \item \textbf{Parameter penalties:} weight decay and norm-based penalties.
  \item \textbf{Stochastic regularization:} dropout and noise injection.
  \item \textbf{Training-procedure regularization:} early stopping, schedules, and augmentation.
  \item \textbf{Balancing-based methods:} full or partial synaptic neural balancing, applied before training or interleaved with training.
\end{itemize}

\subsection{Key questions}
We structure the evaluation around the following questions:
\begin{itemize}
  \item When does each method improve test performance, and by how much?
  \item How do methods differ in their effect on convergence speed and stability?
  \item How sensitive are results to model size and data availability?
  \item How does neural balancing interact with classical regularization?
\end{itemize}

\subsection{Roadmap}
Section~\ref{sec:background} reviews regularization concepts. Section~\ref{sec:methodology} specifies the methods and experimental protocol. Section~\ref{sec:evaluation} reports results, followed by analysis in Section~\ref{sec:discussion}. We close with related work (Section~\ref{sec:related-work}) and conclusions (Section~\ref{sec:conclusion}).

