% Methods and experimental design.

\section{Methodology}
\label{sec:methodology}

\subsection{Compared regularization approaches}
We compare representative approaches commonly used in practice:
\begin{itemize}
  \item \textbf{Weight decay ($L_2$ penalty)} with tuned coefficient.
  \item \textbf{$L_1$ penalty} as a sparsity-inducing baseline.
  \item \textbf{Dropout} with tuned dropout rate.
  \item \textbf{Early stopping} based on validation loss.
  \item \textbf{Synaptic neural balance} as a preprocessing step and as an interleaved procedure.
\end{itemize}

\subsection{Synaptic neural balance (high-level)}
Following \citet{alexos2025synapticbalance}, balancing considers a hidden unit whose incoming weights are scaled by $\lambda>0$ and outgoing weights are scaled by $1/\lambda$. For homogeneous activations, this transformation preserves the network function, while the value of an $L_p$-style weight cost changes with $\lambda$. Balancing chooses $\lambda$ to reduce (or minimize) this cost, resulting in an equalization condition between incoming and outgoing weight ``cost'' for that unit.

\subsection{Evaluation protocol}
Unless otherwise stated, we evaluate each configuration across multiple random seeds and report mean and standard deviation on:
\begin{itemize}
  \item \textbf{Generalization}: test accuracy / test loss.
  \item \textbf{Optimization}: convergence speed (epochs/steps to reach a target metric).
  \item \textbf{Stability}: variance across seeds and sensitivity to hyperparameters.
\end{itemize}

\subsection{Implementation notes}
This report is intended to be reproducible. Hyperparameters and code pointers should be recorded alongside each experiment. Where applicable, we use the same model architecture, data split, optimizer, and training budget across methods to make comparisons fair.

